%===================================== CHAP 4 =================================

\chapter{System Components}
This chapter contains a brief description of the system that has been used.
\section{Software}
This section contain the different software that is used in the x8 system. The control and guidance system is runs on Dune, and the missionplaner on Neptus. The x8 operation system is GLUED. The system is connected to the rtklib whitch is in communitation with DUNE. The internal communication in DUNE is based on IMC messages
\subsection{GLUED}
Glued is a minimal Linux distribution that contain only the necessary packages to run an embedded system. Write why it's used, what is the advantage
\subsection{Dune}
Dune is a runtime environment for unmanned systems on-board software created by LSTS (Underwater Systems and Technology Laboratory) in Porto, Portugal. The enviroment type is called a middleware, whitch is seeing increase usage in unmanned systems. Can refer to ROS or MOOS middleware.

Dune workes by setining up indivitual task that can dispatch and subscribe to different IMC messages. The IMC messages will be explained in \ref{ss:IMC}
A type of middleware. write how to link rtklib with dune
Refer to the dune wiki page
\subsection{IMC}\label{ss:IMC}
Write about the message structure and how it's connected to DUNE. Include how to make new messages.
\subsection{Netpus}
\subsection{Ardupilot}
Ref to Grytes simulator. Remove from thesis
\subsection{RTKLIB}
Rtklib is open source program that can estimate the receiver position based on raw GPS data. It can be used both with a single receiver or differential gps in real time. The setup is based on a base station and a rover. The base station use the str2str app to create a tcp connection with the rovers rtkrcv app.
\subsubsection{rtkrcv}
Rtkrcv is the app program that calculate the position of the rovers antenna. Rtkrcv is configured with a moving baseline in order to get a fixed solution of the position estimate.
\subsubsection{str2str}
Str2str is the app program that retrive the ublox signal from the gps and sends over tcp to the rtkrcv app. The str2str is setup to either send RMTC 3 messages, or whatever is send in from the GPS. Since the str2str do not support to send ublox signal directly. HOw to write that the user should not spesify the input format or the output format.
\section{Physical system}
\subsection{The GPS receiver}
Write about the Ublox LEA M8T gnss receiver. Also include that it support sending GPS and GLONASS data at the same time. Need to be configured.
\cleardoublepage